---
title: "2022 Retained Fish Length Comparisons Expanded"
author: "Melissa H. Monk and Ellie Brauer"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
    pdf_document:
    keep_tex: true
    keep_md: true
toc: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{placeins}
always_allow_html: true
---


```{r load-packages, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(devtools)
library(dplyr)
library(ggplot2)
library(ggridges)
library(stringr)
library(tidyr)
library(unikn)
library(viridis)
library(kableExtra)
library(knitr)
library(xtable)
```



# 2022 fish length comparisons
## Methods
The completed CCFRP database was queried for area, month, day, year, trip, cell, site (from the drift table not the trip table), species, length, tag, and retained. Desired areas (and species optional) were selected based on institution of interest. Data was then transfered to an excel spreadsheet and a length column in mm units was created by multiplying the cm length column by 10. R friendly column names (area, month, day,	year, vessel, trip, cell, site, species, length_mm, length_cm, tag, retained) were created.

In R, species with large sample sizes and species of interest were identified. An institution and species specific dataframe was created by filtering for REF site and species. Year and retained variables were changed to characters. Density plots with mean lines for each species and year that displays the distribution of lengths of retained fish and non-retained fish were created. A summary table of retained and non-retained fish for each year was produced and diplayed below the corresponding graph. 

Length measurement techniques: Cal Poly Humboldt: "Pinch" tail for Canary, Blue, Deacon RF., measure natural splay for other species. Cal Poly Slo, Fork Length. BML, Fork Length. MLML, Natural Splay Total Length. SIO, Natural Splay Total Length. UCSB, Natural Splay Total Length.

\newpage
## Cal Poly Piedras Blancas Blue Rockfish
```{r echo = FALSE, include = FALSE, warning = FALSE, message = FALSE}
poly = read.csv("poly_ref.csv")
head(poly)
polyblue = filter(poly, species == "BLU")
polyblue$year = as.character(polyblue$year)
polyblue$retained = as.character(polyblue$retained)
polyblueBL = filter(polyblue, area == "BL")
meangroup = polyblueBL %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
```

```{r, echo= FALSE, message=FALSE, warning=FALSE}
ggplot(polyblueBL, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polyblueBL %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Blue RF Piedras Blancas",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```

## Cal Poly Point Buchon Blue Rockfish
```{r echo = FALSE, include = FALSE, warning = FALSE, message = FALSE}
poly = read.csv("poly_ref.csv")
head(poly)
polyblue = filter(poly, species == "BLU")
polyblue$year = as.character(polyblue$year)
polyblue$retained = as.character(polyblue$retained)
polybluePB = filter(polyblue, area == "PB")
meangroup = polybluePB  %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
```

```{r, echo= FALSE, message=FALSE, warning=FALSE}
ggplot(polybluePB, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polybluePB %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Blue RF Point Buchon",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```


\newpage
## Cal Poly Slo Piedras Blancas Gopher Rockfish
```{r, echo= FALSE, message=FALSE}
polygoph = filter(poly, species == "GPR")
polygoph$year = as.character(polygoph$year)
polygoph$retained = as.character(polygoph$retained)
polygophBL = filter(polygoph, area == "BL")
meangroup = polygophBL %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(polygophBL, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polygophBL %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Gopher RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```

\newpage
## Cal Poly Slo Point Buchon Gopher Rockfish
```{r, echo= FALSE, message=FALSE}
polygoph = filter(poly, species == "GPR")
polygoph$year = as.character(polygoph$year)
polygoph$retained = as.character(polygoph$retained)
polygophPB = filter(polygoph, area == "PB")
meangroup = polygophPB %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(polygophPB, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polygophPB %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Gopher RF Point Buchon",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```


\newpage
## Cal Poly Slo Piedras Blancas Copper Rockfish
```{r, echo= FALSE, message=FALSE}
polycop = filter(poly, species == "CPR")
polycop$year = as.character(polycop$year)
polycop$retained = as.character(polycop$retained)
polycopBL = filter(polycop, area == "BL")
meangroup = polycopBL %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(polycopBL, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polycopBL %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Copper RF Piedras Blancas",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```

\newpage
## Cal Poly Slo Point Buchon Copper Rockfish
```{r, echo= FALSE, message=FALSE}
polycop = filter(poly, species == "CPR")
polycop$year = as.character(polycop$year)
polycop$retained = as.character(polycop$retained)
polycopPB = filter(polycop, area == "PB")
meangroup = polycopPB %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(polycopPB, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polycopPB %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Copper RF Point Buchon",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```

\newpage
## Cal Poly Slo Piedras Blancas Vermilion Rockfish
```{r, echo= FALSE, message=FALSE, warning=FALSE}
polyverm = filter(poly, species == "VER")
polyverm$year = as.character(polyverm$year)
polyverm$retained = as.character(polyverm$retained)
polyvermBL = filter(polyverm, area == "BL")
meangroup = polyvermBL %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(polyvermBL, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polyvermBL %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Vermilion RF Piedras Blancas",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```

\newpage
## Cal Poly Slo Point Buchon Vermilion Rockfish
```{r, echo= FALSE, message=FALSE, warning=FALSE}
polyverm = filter(poly, species == "VER")
polyverm$year = as.character(polyverm$year)
polyverm$retained = as.character(polyverm$retained)
polyvermPB = filter(polyverm, area == "PB")
meangroup = polyvermPB %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(polyvermPB, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polyvermPB %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Vermilion RF Piedras Blancas",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```

\newpage
## Cal Poly Slo Piedras Blancas Olive Rockfish
```{r, echo= FALSE, message=FALSE}
polyolive = filter(poly, species == "OLV")
polyolive$year = as.character(polyolive$year)
polyolive$retained = as.character(polyolive$retained)
polyoliveBL = filter(polyolive, area == "BL")
meangroup = polyoliveBL %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(polyoliveBL, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polyoliveBL %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Olive Rockfish Piedras Blancas",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```

\newpage
## Cal Poly Slo Point Buchon Olive Rockfish
```{r, echo= FALSE, message=FALSE}
polyolive = filter(poly, species == "OLV")
polyolive$year = as.character(polyolive$year)
polyolive$retained = as.character(polyolive$retained)
polyolivePB = filter(polyolive, area == "PB")
meangroup = polyolivePB %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(polyolivePB, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = polyolivePB %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Slo Olive Rockfish Point Buchon",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```


\newpage
## BML Bodega Head Black Rockfish
```{r, echo= FALSE, message=FALSE}
bod = read.csv("bod.csv")
bod = filter(bod, (site) == "REF")
bodblack = filter(bod, species == "BLA")
bodblack$year = as.character(bodblack$year)
bodblack$retained = as.character(bodblack$retained)
bodblackBH = filter(bodblack, area == "BH")
meangroup = bodblackBH %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(bodblackBH, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = bodblackBH %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "BML Black RF Bodega Head",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```

\newpage
## BML Stewarts Point Black Rockfish
```{r, echo= FALSE, message=FALSE}
bod = read.csv("bod.csv")
bod = filter(bod, (site) == "REF")
bodblack = filter(bod, species == "BLA")
bodblack$year = as.character(bodblack$year)
bodblack$retained = as.character(bodblack$retained)
bodblackSP = filter(bodblack, area == "SP")
meangroup = bodblackSP %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(bodblackSP, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = bodblackSP %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "BML Black RF Stewarts Point",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```


\newpage
## BML Bodega Head Deacon Rockfish
```{r, echo= FALSE, message=FALSE}
bod = read.csv("bod.csv")
bod = filter(bod, (site) == "REF")
boddeac = filter(bod, species == "DEA")
boddeac$year = as.character(boddeac$year)
boddeac$retained = as.character(boddeac$retained)
meangroup = boddeac %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(boddeac, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = boddeac %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "BML Deacon RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## BML Blue Rockfish
```{r, echo= FALSE, message=FALSE}
bod = read.csv("bod.csv")
bod = filter(bod, (site) == "REF")
bodblue = filter(bod, species == "BLU")
bodblue$year = as.character(bodblue$year)
bodblue$retained = as.character(bodblue$retained)
meangroup = bodblue %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(bodblue, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = bodblue %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "BML Blue RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## BML Gopher Rockfish
```{r, echo= FALSE, message=FALSE}
bod = read.csv("bod.csv")
bod = filter(bod, (site) == "REF")
bodgoph = filter(bod, species == "GPR")
bodgoph$year = as.character(bodgoph$year)
bodgoph$retained = as.character(bodgoph$retained)
meangroup = bodgoph %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(bodgoph, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = bodgoph %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "BML Gopher RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## BML Yellowtail Rockfish
```{r, echo= FALSE, message=FALSE}
bod = read.csv("bod.csv")
bod = filter(bod, (site) == "REF")
bodyel = filter(bod, species == "YTL")
bodyel$year = as.character(bodyel$year)
bodyel$retained = as.character(bodyel$retained)
meangroup = bodyel %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(bodyel, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = bodyel %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "BML Yellowtail RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## BML Copper Rockfish
```{r, echo= FALSE, message=FALSE}
bod = read.csv("bod.csv")
bod = filter(bod, (site) == "REF")
bodcop = filter(bod, species == "CPR")
bodcop$year = as.character(bodcop$year)
bodcop$retained = as.character(bodcop$retained)
meangroup = bodcop %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(bodcop, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = bodcop %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "BML Copper RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## BML Canary Rockfish
```{r, echo= FALSE, message=FALSE}
bod = read.csv("bod.csv")
bod = filter(bod, (site) == "REF")
bodcan = filter(bod, species == "CNY")
bodcan$year = as.character(bodcan$year)
bodcan$retained = as.character(bodcan$retained)
meangroup = bodcan %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(bodcan, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = bodcan %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "BML Cannary RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## UCSB Blue Rockfish
```{r, echo= FALSE, message=FALSE}
ucsb = read.csv("UCSB.csv")
ucsb = filter(ucsb, (site) == "REF")
ucsbblue = filter(ucsb, species == "BLU", year == "2022")
ucsbblue$year = as.character(ucsbblue$year)
ucsbblue$retained = as.character(ucsbblue$retained)
meangroup = ucsbblue %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(ucsbblue, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = ucsbblue %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "UCSB Blue RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## UCSB Copper Rockfish
```{r, echo= FALSE, message=FALSE}
ucsb = read.csv("UCSB.csv")
ucsb = filter(ucsb, (site) == "REF")
ucsbcop = filter(ucsb, species == "BLU", year == "2022")
ucsbcop$year = as.character(ucsbcop$year)
ucsbcop$retained = as.character(ucsbcop$retained)
meangroup = ucsbcop %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(ucsbcop, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = ucsbcop %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "UCSB Copper RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## UCSB Gopher Rockfish
```{r, echo= FALSE, message=FALSE}
ucsb = read.csv("UCSB.csv")
ucsb = filter(ucsb, (site) == "REF")
ucsbgoph = filter(ucsb, species == "GPR", year == "2022")
ucsbgoph$year = as.character(ucsbgoph$year)
ucsbgoph$retained = as.character(ucsbgoph$retained)
meangroup = ucsbgoph %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(ucsbgoph, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = ucsbcop %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "UCSB Gopher RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## Cal Poly Humboldt Black Rockfish
```{r, echo= FALSE, message=FALSE}
hsu = read.csv("HSU.csv")
hsu = filter(hsu, (site) == "REF")
hsublack = filter(hsu, species == "BLA")
hsublack$year = as.character(hsublack$year)
hsublack$retained = as.character(hsublack$retained)
meangroup = hsublack %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(hsublack, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = hsublack %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Humboldt Black RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## Cal Poly Humboldt Deacon Rockfish
```{r, echo= FALSE, message=FALSE, warning=FALSE}
hsu = read.csv("HSU.csv")
hsu = filter(hsu, (site) == "REF")
hsudea = filter(hsu, species == "DEA")
hsudea$year = as.character(hsudea$year)
hsudea$retained = as.character(hsudea$retained)
meangroup = hsudea %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(hsudea, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = hsudea %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Humboldt Deacon RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## Cal Poly Humboldt Yellowtail Rockfish
```{r, echo= FALSE, message=FALSE}
hsu = read.csv("HSU.csv")
hsu = filter(hsu, (site) == "REF")
hsuytl = filter(hsu, species == "YTL")
hsuytl$year = as.character(hsuytl$year)
hsuytl$retained = as.character(hsuytl$retained)
meangroup = hsuytl %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(hsuytl, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = hsuytl %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "Cal Poly Humboldt Yellowtail RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## MLML Black Rockfish
```{r, echo= FALSE, message=FALSE}
moss = read.csv("MLML.csv")
moss = filter(moss, (site) == "REF")
mossblack = filter(moss, species == "BLA")
mossblack$year = as.character(mossblack$year)
mossblack$retained = as.character(mossblack$retained)
meangroup = mossblack %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(mossblack, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = mossblack %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "MLML Black RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## MLML Copper Rockfish
```{r, echo= FALSE, message=FALSE, warning=FALSE}
moss = read.csv("MLML.csv")
moss = filter(moss, (site) == "REF")
mosscop = filter(moss, species == "CPR")
mosscop$year = as.character(mosscop$year)
mosscop$retained = as.character(mosscop$retained)
meangroup = mosscop %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(mosscop, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = mosscop %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "MLML Copper RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```
\newpage
## MLML Blue Rockfish
```{r, echo= FALSE, message=FALSE, warning=FALSE}
moss = read.csv("MLML.csv")
moss = filter(moss, (site) == "REF")
mossblu = filter(moss, species == "CPR")
mossblu$year = as.character(mossblu$year)
mossblu$retained = as.character(mossblu$retained)
meangroup = mossblu %>% group_by(year, retained) %>% 
  summarise(avg = mean(length_mm))
ggplot(mossblu, aes(x=length_mm, fill=retained)) + geom_density(alpha=.2)+ 
  facet_grid(year ~ .) + 
  geom_vline(data=meangroup, aes(xintercept=avg, colour=retained), linetype="dashed", size=.3) + theme_bw() + theme(panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

```{r, results = "asis", echo= FALSE, message=FALSE}
tab = mosscop %>% group_by(year, retained) %>% 
  summarise(n = n()) %>% pivot_wider(names_from = retained, values_from = n)
kableExtra::kbl(tab,
                longtable = TRUE,
  booktabs = TRUE,
  caption = "MLML Blue RF",
  row.names = F
) %>%
  kable_styling(latex_options=c("repeat_header", "striped", "hold_position"))
```